SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-12 frontrunning/Latex/sections/paper.tex
[frontrunning] ENS stuff

Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount . Also note that if two bidders bid the same price, the first to reveal wins it~\cite{ENSHandlingFrontRunningDiscussion}. Combined with the leaked information, this introduces a race condition which could be mitigated if bidding time was taken into effect instead of solely reveal time.

Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal. (2) Attacker is speculating, which he will bid with a slightly higher value %so he waits to see other reveal, then insert myself with the information from the other reveal. (3) If my amount is bigger, I see other reveal and then reveal.

Sealed bids could easily be identified from the recent transactions --> depends on the anonymity set

Displacement attack <--

%A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.

Also using the leaked information, the front-running attack vector mimics the traditional domain front-running attacks. The auction model is similar to open auctions in \ref{sec:cryptogames}.

@@

%Shayan -> Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

@@

\section{Concluding Remarks}

>>>>

Users are allowed to bid for 3 days before the 2-day reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount . Also note that if two bidders bid the same price, the first to reveal wins it~\cite{ENSHandlingFrontRunningDiscussion}. Using the leaked information, the domain squatter can win the auction with the same price of the original bidder by revealing it first. This is similar to front-running as it relies on inserting an action before the user, however we do not consider this specific action as front-running attack.

@@

%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

@@

%Jeremy TODO
\section{Concluding Remarks}
